### 2009-05-26 doc/internal_notes/client/GUI_LAP_plans.tex
Update of text

A new and updated version of LAP is presently under development which will make the LAP to Web 2.0 compliant and which will interface to the next generation ARC client library. The latter interfacing is done in collaboration between LAP and the KnowARC project and will allow the KnowARC project to use the next generation LAP for it's deliverable D2.2-2 "Advanced graphical client with easy-to-use job creation module and support for bulk job management and monitoring".

@@

\begin{itemize}
\item{The portal will support bulk job handling, i.e. it will support listing and sorting of (several) hundred(s) of jobs using a java table. Using the same table bulk handling will be enabled making it possible to select groups of jobs to execute commands on like e.g. kill, clean, get, resume etc. Will it be possible to group jobs together?}
\item{Job statuses will be updated automatically by a background processes, but a "manual update" button will also be provided.}
\item{Job "babysitting" will offer to automatically download finished jobs or resubmit jobs that have failed. Resubmission will be limited to only 2(3?) attempts. It will be possible to activate "babysitting" at any time for any kind of job.}
\item{Users will be able to create and maintain lists of favorite clusters. Blacklisting of clusters will also be possible.}
\item{The LAP is application orieented and new grid jobs are created through an application specific interface. The new and updated version of LAP will offer an application unspecific interface allowing users to create any kind of grid job. The interface will offer the user an easy to use job description creation module and the possibility to upload executable and job input files.}
\item{Occasionally users would like to use existing job description files, but still submit their grid job through the LAP. To support this the LAP will offer an interface for uploading and submitting job description files.}
\end{itemize}

>>>>

A new and updated version of LAP is presently under development which
will make use of Web 2.0 features and which will interface to the next
generation ARC client library. The latter interfacing is done in
collaboration between LAP and the KnowARC project and will allow the
KnowARC project to use the next generation LAP for it's deliverable
D2.2-2 "Advanced graphical client with easy-to-use job creation module
and support for bulk job management and monitoring".

@@

\begin{itemize}
\item{The portal will support bulk job handling, i.e. it will support
  listing and sorting of (several) hundred(s) of jobs using a
  table. Using the same table bulk handling will be enabled making it
  possible to select groups of jobs to execute commands on like
  e.g. kill, clean, get, resume etc. }
\item{Job statuses will be updated automatically by a background
  processes, but a "manual update" button will also be provided.}
\item{Job "babysitting" will offer to automatically download finished
  jobs or resubmit jobs that have failed. Resubmission will be limited
  to only 2(3?) attempts. It will be possible to activate
  "babysitting" at any time for any kind of job.}
\item{Users will be able to create and maintain lists of favorite
  clusters. Blacklisting of clusters will also be possible.}
\item{The LAP is application orieented and new grid jobs are created
  through an application specific interface. The new and updated
  version of LAP will offer an application unspecific interface
  allowing users to create any kind of grid job. The interface will
  offer the user an easy to use job description creation module and
  the possibility to upload executable and job input files.}
\item{Occasionally users would like to use existing job description
  files, but still submit their grid job through the LAP. To support
  this the LAP will offer an interface for uploading and submitting
  job description files.}
\end{itemize}
